Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
second stage soundness restoration

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
uses a two-stage verification such that in the first stage it 
assumes a certain precision \param{I_b}{F_b}, whose 
soundness is checked in the second verification stage.

>>>>

The second approach is illustrated in Fig.~\ref{fig:CEGIS} and 
uses a two-stage verification with a first stage that performs unsound fixed point operations given the precision \param{I_b}{F_b}, and a second stage that restores soundness by validating these operations using interval arithmetic on the synthesised plant.
